---
title: "ciruitscape" 

author:
    - name: "Moritz Wenzler-Meya"
      url: 
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 
    - name: "Stephanie Kramer-Schadt"
      url: 
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id:
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate      
        code_folding: false  
        toc: true            
        toc_depth: 2        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
                      dev = "ragg_png", fig.width = 9, fig.height = 6, dpi = 600, retina = 1)
Sys.setlocale("LC_TIME", "C")
```

# Setup

```{r packages}
sapply(list("sf", "tidyverse", "terra", "here", "raster", 
            "sp", "ggplot2", "ggnewscale", "viridis", "stars"), 
       library, character.only = TRUE, logical.return = TRUE)
```

We provide code for the old "circuitscape 4" using python language and the recent "circuitscape 5" using julia. 

We provide these two code parts because the code for "circuitscape 4" was prepared in 2017 is not running anymore on our new machines. 

You can use the ".ini" files from "circuitscape 4" also for "circuitscape 5". See "circuitscape.org".


# Circuitscape 4

## path to circuitscape 4

```{r}
# Make a place holder for the cs_run.exe path
# Don't forget the "Program Files" problem. Please install circuitscape 4 directly under "C:" on your machine. 
# The folder "Program Files" has a space in the name and circuitscape may not run because of that.

CS_exe <- "C:/Circuitscape/cs_run.exe"
```


## run circuitscape for hsi 2020
```{r}
spec_no_to_sim <- c(5,49)# c(1:81) # max 81  
scenario <- 'hsi_2020' 
scenario_out <- 'cs_2020'
folder_simu <- "circuitscape_2020" 

if (file.exists(here("data", "processed", folder_simu)) == FALSE) {
  dir.create(here("data", "processed", folder_simu))
} else {print('OBS Folder Exists!') }

# loop for circuitscape 

for (i in spec_no_to_sim){ 
  if (file.exists(here("data", "processed", folder_simu, paste0(scenario_out, "_species_" ,i))) == FALSE) {
  dir.create(here("data", "processed", folder_simu, paste0(scenario_out, "_species_" ,i)))
  } else {print('OBS Folder Exists!') }
  
  ## output names
  cs_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.out'))              # name of map
  hsi_path <- here('data', 'raw', 'hsi_maps', scenario, paste0(scenario, '_species_' ,i, '.asc'))       # name of cost raster
  ini_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.ini'))       # name of ini file
  
  # Make an .ini file
  CS_ini <- c("[Calculation options]",
              "low_memory_mode = False",
              " parallelize = False",
              "solver = cg+amg",
              "print_timings = False",
              "preemptive_memory_release = False",
              "print_rusages = False",
              "max_parallel = 0",
              "[Output options]",
              "set_focal_node_currents_to_zero = True",
              "write_cur_maps = True",
              "write_cum_cur_map_only = True",
              "log_transform_maps = False",
              "write_max_cur_maps = False",
              "[Version]",
              "version = 4.0.5",
              "[Options for pairwise and one-to-all and all-to-one modes]",
              "included_pairs_file = (Browse for a file with pairs to include or exclude)",
              "use_included_pairs = False",
              "[Habitat raster or graph]",
              "habitat_map_is_resistances = False",
              "[Circuitscape mode]",
              "data_type = raster",
              "scenario = all-to-one",
              paste(c("point_file =",
                      "habitat_file =",
                      "output_file ="),
                    paste(c(here("data", "raw", "node_123.asc"),
                            hsi_path,
                            cs_path),sep="/")))
              
              
              # Write it to your working directory
              writeLines(CS_ini, ini_path)
              
              # Make the CS run cmd
              CS_run <- paste(CS_exe, ini_path) # Make the cmd
              
              # Run the command
             system(CS_run)
              
}

```

## run circuitscape for hsi 2050

```{r}
spec_no_to_sim <- c(5,49)#c(1:81) # max 81  
scenario <- 'hsi_2050' 
scenario_out <- 'cs_2050'
folder_simu <- "circuitscape_2050" 

if (file.exists(here("data", "processed", folder_simu)) == FALSE) {
  dir.create(here("data", "processed", folder_simu))
} else {print('OBS Folder Exists!') }

# loop for circuitscape 

for (i in spec_no_to_sim){ 
  if (file.exists(here("data", "processed", folder_simu, paste0(scenario_out, "_species_" ,i))) == FALSE) {
  dir.create(here("data", "processed", folder_simu, paste0(scenario_out, "_species_" ,i)))
  } else {print('OBS Folder Exists!') }
  
  ## output names
  cs_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.out'))              # name of map
  hsi_path <- here('data', 'raw', 'hsi_maps', scenario, paste0(scenario, '_species_' ,i, '.asc'))       # name of cost raster
  ini_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.ini'))       # name of ini file
  
  # Make an .ini file
  CS_ini <- c("[Calculation options]",
              "low_memory_mode = False",
              " parallelize = False",
              "solver = cg+amg",
              "print_timings = False",
              "preemptive_memory_release = False",
              "print_rusages = False",
              "max_parallel = 0",
              "[Output options]",
              "set_focal_node_currents_to_zero = True",
              "write_cur_maps = True",
              "write_cum_cur_map_only = True",
              "log_transform_maps = False",
              "write_max_cur_maps = False",
              "[Version]",
              "version = 4.0.5",
              "[Options for pairwise and one-to-all and all-to-one modes]",
              "included_pairs_file = (Browse for a file with pairs to include or exclude)",
              "use_included_pairs = False",
              "[Habitat raster or graph]",
              "habitat_map_is_resistances = False",
              "[Circuitscape mode]",
              "data_type = raster",
              "scenario = all-to-one",
              paste(c("point_file =",
                      "habitat_file =",
                      "output_file ="),
                    paste(c(here("data", "raw", "node_123.asc"),
                            hsi_path,
                            cs_path),sep="/")))
              
              
              # Write it to your working directory
              writeLines(CS_ini, ini_path)
              
              # Make the CS run cmd
              CS_run <- paste(CS_exe, ini_path) # Make the cmd
              
              # Run the command
             system(CS_run)
              
}

```


## run circuitscape for hsi 2080

```{r}
spec_no_to_sim <- c(5,49)#c(1:81) # max 81  
scenario <- 'hsi_2080' 
scenario_out <- 'cs_2080'
folder_simu <- "circuitscape_2080" 

if (file.exists(here("data", "processed", folder_simu)) == FALSE) {
  dir.create(here("data", "processed", folder_simu))
} else {print('OBS Folder Exists!') }

# loop for circuitscape 

for (i in spec_no_to_sim){ 
  if (file.exists(here("data", "processed", folder_simu, paste0(scenario_out, "_species_" ,i))) == FALSE) {
  dir.create(here("data", "processed", folder_simu, paste0(scenario_out, "_species_" ,i)))
  } else {print('OBS Folder Exists!') }
  
  ## output names
  cs_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.out'))              # name of map
  hsi_path <- here('data', 'raw', 'hsi_maps', scenario, paste0(scenario, '_species_' ,i, '.asc'))       # name of cost raster
  ini_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.ini'))       # name of ini file
  
  # Make an .ini file
  CS_ini <- c("[Calculation options]",
              "low_memory_mode = False",
              " parallelize = False",
              "solver = cg+amg",
              "print_timings = False",
              "preemptive_memory_release = False",
              "print_rusages = False",
              "max_parallel = 0",
              "[Output options]",
              "set_focal_node_currents_to_zero = True",
              "write_cur_maps = True",
              "write_cum_cur_map_only = True",
              "log_transform_maps = False",
              "write_max_cur_maps = False",
              "[Version]",
              "version = 4.0.5",
              "[Options for pairwise and one-to-all and all-to-one modes]",
              "included_pairs_file = (Browse for a file with pairs to include or exclude)",
              "use_included_pairs = False",
              "[Habitat raster or graph]",
              "habitat_map_is_resistances = False",
              "[Circuitscape mode]",
              "data_type = raster",
              "scenario = all-to-one",
              paste(c("point_file =",
                      "habitat_file =",
                      "output_file ="),
                    paste(c(here("data", "raw", "node_123.asc"),
                            hsi_path,
                            cs_path),sep="/")))
              
              
              # Write it to your working directory
              writeLines(CS_ini, ini_path)
              
              # Make the CS run cmd
              CS_run <- paste(CS_exe, ini_path) # Make the cmd
              
              # Run the command
             system(CS_run)
              
}

```

# Circuitscape 5

## prepare julia for circuitscape 5

```{r}
library(JuliaCall)
#julia_setup(install = TRUE) # only first time
#julia_install_package_if_needed("Circuitscape") # only first time
julia_library("Circuitscape")
```


## run circuitscape for hsi 2020
```{r}
spec_no_to_sim <- c(5,49)# c(1:81) # max 81  
scenario <- 'hsi_2020' 
scenario_out <- 'cs_2020'
folder_simu <- "circuitscape_2020" 

if (file.exists(here("data", "processed", folder_simu)) == FALSE) {
  dir.create(here("data", "processed", folder_simu))
} else {print('OBS Folder Exists!') }

# loop for circuitscape 

for (i in spec_no_to_sim){ 
  
  if (file.exists(here("data", "processed", paste0(scenario_out, "_species_" ,i))) == FALSE) {
  dir.create(here("data", "processed", paste0(scenario_out, "_species_" ,i)))
  } else {print('OBS Folder Exists!') }
  
  ## output names
  cs_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.out'))              # name of map
  hsi_path <- here('data', 'raw', 'hsi_maps', scenario, paste0(scenario, '_species_' ,i, '.asc'))       # name of cost raster
  ini_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.ini'))       # name of ini file
  
  # Make an .ini file
  CS_ini_j <- c("[Options for advanced mode]",
        "ground_file_is_resistances = False",
        "source_file = (Browse for a current source file)",
        "remove_src_or_gnd = keepall",
        "ground_file = (Browse for a ground point file)",
        "use_unit_currents = False",
        "use_direct_grounds = False",
        "[Calculation options]",
        "parallelize = TRUE",
        "low_memory_mode = False",
        "solver = cg+amg",
        "max_parallel = 20", # set the number of cores you want to use
        "print_timings = False",
        "[Options for pairwise and one-to-all and all-to-one modes]",
        "included_pairs_file = None",
        "use_included_pairs = False",
        paste0("point_file = ", here("data", "raw", "node_123.asc")),
        "[Output options]",
        "write_cum_cur_map_only = True",
        "log_transform_maps = False",
         paste0("output_file = ", cs_path),
        "write_max_cur_maps = False",
        "write_volt_maps = False",
        "set_null_currents_to_nodata = True",
        "set_null_voltages_to_nodata = False",
        "compress_grids = False",
        "write_cur_maps = True",
        "[Short circuit regions (aka polygons)]",
        "use_polygons = False",
        "polygon_file = (Browse for a current source file)",
        "[Connection scheme for raster habitat data]",
        "connect_four_neighbors_only = True",
        "connect_using_avg_resistances = False",
        "[Habitat raster or graph]",
        paste0("habitat_file = ", hsi_path),
        "habitat_map_is_resistances = False",
        "[Options for one-to-all and all-to-one modes]",
        "use_variable_source_strengths = False",
        "variable_source_file = None",
        "[Version]",
        "version = 5.13.3",
        "[Mask file]",
        "use_mask = False",
        "mask_file = None",
        "[Circuitscape mode]",
        "data_type = raster",
        "scenario = all-to-one"
              )
  
              # Write it to your working directory
              writeLines(CS_ini_j, ini_path)
              
              # Run the command
             julia_call("compute", ini_path)
              
}

```

## run circuitscape for hsi 2050

```{r}
spec_no_to_sim <- c(5,49)#c(1:81) # max 81  
scenario <- 'hsi_2050' 
scenario_out <- 'cs_2050'
folder_simu <- "circuitscape_2050" 

if (file.exists(here("data", "processed", folder_simu)) == FALSE) {
  dir.create(here("data", "processed", folder_simu))
} else {print('OBS Folder Exists!') }

# loop for circuitscape 

for (i in spec_no_to_sim){ 
  
  if (file.exists(here("data", "processed", paste0(scenario_out, "_species_" ,i))) == FALSE) {
  dir.create(here("data", "processed", paste0(scenario_out, "_species_" ,i)))
  } else {print('OBS Folder Exists!') }
  
  ## output names
  cs_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.out'))              # name of map
  hsi_path <- here('data', 'raw', 'hsi_maps', scenario, paste0(scenario, '_species_' ,i, '.asc'))       # name of cost raster
  ini_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.ini'))       # name of ini file
  
  # Make an .ini file
  CS_ini_j <- c("[Options for advanced mode]",
        "ground_file_is_resistances = False",
        "source_file = (Browse for a current source file)",
        "remove_src_or_gnd = keepall",
        "ground_file = (Browse for a ground point file)",
        "use_unit_currents = False",
        "use_direct_grounds = False",
        "[Calculation options]",
        "parallelize = TRUE",
        "low_memory_mode = False",
        "solver = cg+amg",
        "max_parallel = 20", # set the number of cores you want to use
        "print_timings = False",
        "[Options for pairwise and one-to-all and all-to-one modes]",
        "included_pairs_file = None",
        "use_included_pairs = False",
        paste0("point_file = ", here("data", "raw", "node_123.asc")),
        "[Output options]",
        "write_cum_cur_map_only = True",
        "log_transform_maps = False",
         paste0("output_file = ", cs_path),
        "write_max_cur_maps = False",
        "write_volt_maps = False",
        "set_null_currents_to_nodata = True",
        "set_null_voltages_to_nodata = False",
        "compress_grids = False",
        "write_cur_maps = True",
        "[Short circuit regions (aka polygons)]",
        "use_polygons = False",
        "polygon_file = (Browse for a current source file)",
        "[Connection scheme for raster habitat data]",
        "connect_four_neighbors_only = True",
        "connect_using_avg_resistances = False",
        "[Habitat raster or graph]",
        paste0("habitat_file = ", hsi_path),
        "habitat_map_is_resistances = False",
        "[Options for one-to-all and all-to-one modes]",
        "use_variable_source_strengths = False",
        "variable_source_file = None",
        "[Version]",
        "version = 5.13.3",
        "[Mask file]",
        "use_mask = False",
        "mask_file = None",
        "[Circuitscape mode]",
        "data_type = raster",
        "scenario = all-to-one"
              )
  
              # Write it to your working directory
              writeLines(CS_ini_j, ini_path)
              
              # Run the command
             julia_call("compute", ini_path)
              
}

```


## run circuitscape for hsi 2080

```{r}
spec_no_to_sim <- c(5,49)#c(1:81) # max 81  
scenario <- 'hsi_2080' 
scenario_out <- 'cs_2080'
folder_simu <- "circuitscape_2080" 

if (file.exists(here("data", "processed", folder_simu)) == FALSE) {
  dir.create(here("data", "processed", folder_simu))
} else {print('OBS Folder Exists!') }

# loop for circuitscape 

for (i in spec_no_to_sim){ 
  
  if (file.exists(here("data", "processed", paste0(scenario_out, "_species_" ,i))) == FALSE) {
  dir.create(here("data", "processed", paste0(scenario_out, "_species_" ,i)))
  } else {print('OBS Folder Exists!') }
  
  ## output names
  cs_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.out'))              # name of map
  hsi_path <- here('data', 'raw', 'hsi_maps', scenario, paste0(scenario, '_species_' ,i, '.asc'))       # name of cost raster
  ini_path <- here("data", "processed", 
                      folder_simu, 
                      paste0(scenario_out, "_species_" ,i), 
                      paste0('circuitscape_ini_',scenario_out, "_species_" ,i, '.ini'))       # name of ini file
  
  # Make an .ini file
  CS_ini_j <- c("[Options for advanced mode]",
        "ground_file_is_resistances = False",
        "source_file = (Browse for a current source file)",
        "remove_src_or_gnd = keepall",
        "ground_file = (Browse for a ground point file)",
        "use_unit_currents = False",
        "use_direct_grounds = False",
        "[Calculation options]",
        "parallelize = TRUE",
        "low_memory_mode = False",
        "solver = cg+amg",
        "max_parallel = 20", # set the number of cores you want to use
        "print_timings = False",
        "[Options for pairwise and one-to-all and all-to-one modes]",
        "included_pairs_file = None",
        "use_included_pairs = False",
        paste0("point_file = ", here("data", "raw", "node_123.asc")),
        "[Output options]",
        "write_cum_cur_map_only = True",
        "log_transform_maps = False",
         paste0("output_file = ", cs_path),
        "write_max_cur_maps = False",
        "write_volt_maps = False",
        "set_null_currents_to_nodata = True",
        "set_null_voltages_to_nodata = False",
        "compress_grids = False",
        "write_cur_maps = True",
        "[Short circuit regions (aka polygons)]",
        "use_polygons = False",
        "polygon_file = (Browse for a current source file)",
        "[Connection scheme for raster habitat data]",
        "connect_four_neighbors_only = True",
        "connect_using_avg_resistances = False",
        "[Habitat raster or graph]",
        paste0("habitat_file = ", hsi_path),
        "habitat_map_is_resistances = False",
        "[Options for one-to-all and all-to-one modes]",
        "use_variable_source_strengths = False",
        "variable_source_file = None",
        "[Version]",
        "version = 5.13.3",
        "[Mask file]",
        "use_mask = False",
        "mask_file = None",
        "[Circuitscape mode]",
        "data_type = raster",
        "scenario = all-to-one"
              )
  
              # Write it to your working directory
              writeLines(CS_ini_j, ini_path)
              
              # Run the command
             julia_call("compute", ini_path)
              
}

```

# plot 

## just for plotting

```{r}
nodes_all <- st_read(here("data", "raw", "nodes_all.gpkg"))

ras_mask <- rast(here::here("data", "raw", "hsi_maps", "hsi_2020", "hsi_2020_species_5.asc"))
```

## load data back in and plot them directly

### 2020
```{r}
circuitscape_2020_l <- lapply(c(5,49), function(x){
  ras <- rast(list.files(
    path = here::here("data",
                      "processed",
                      "circuitscape_2020"),
    pattern = paste0(x, "_cum_curmap.asc$"),
    full.names = TRUE,
    recursive = TRUE
  ))
  ras_m <- mask(ras, nodes_all, inverse = TRUE)
  ras_m_1000 <- (ras_m/max(values(ras_m), na.rm = T)*1000) |> mask(ras_mask)
  
  ggplot() + 
  stars::geom_stars(data = stars::st_as_stars(ras_m_1000)) + 
  scale_fill_gradientn(
     colours = viridis::viridis(10),
     values = scales::rescale(quantile(values(ras_m_1000),
                              probs = seq(0, 1, 0.1),
                                       na.rm = T)),
    na.value = "transparent", 
    name = "") + 
      ggplot2::coord_sf(expand = FALSE) +
    ggnewscale::new_scale_fill() +
  geom_sf(data = nodes_all, fill = "grey70", color = NA) +  
   ggtitle("Circuitscape Maps 2020") + 
  theme_void()

ggsave(here("plots", "circuitscape_plots_2020", paste0("circuitscape_2020_sp", x,".png")), dpi = 300)
})


```

### 2050
```{r}
circuitscape_2050_l <- lapply(c(5,49), function(x){
  ras <- rast(list.files(
    path = here::here("data",
                      "processed",
                      "circuitscape_2050"),
    pattern = paste0(x, "_cum_curmap.asc$"),
    full.names = TRUE,
    recursive = TRUE
  ))
  ras_m <- mask(ras, nodes_all, inverse = TRUE)
  ras_m_1000 <- (ras_m/max(values(ras_m), na.rm = T)*1000) |> mask(ras_mask)
  
  ggplot() + 
  stars::geom_stars(data = stars::st_as_stars(ras_m_1000)) + 
  scale_fill_gradientn(
     colours = viridis::viridis(10),
     values = scales::rescale(quantile(values(ras_m_1000),
                              probs = seq(0, 1, 0.1),
                                       na.rm = T)),
    na.value = "transparent", 
    name = "") + 
      ggplot2::coord_sf(expand = FALSE) +
    ggnewscale::new_scale_fill() +
  geom_sf(data = nodes_all, fill = "grey70", color = NA) +  
   ggtitle("Circuitscape Maps 2050") + 
  theme_void()

ggsave(here("plots", "circuitscape_plots_2050", paste0("circuitscape_2050_sp", x,".png")), dpi = 300)
})


```

### 2080
```{r}
circuitscape_2080_l <- lapply(c(5,49), function(x){
  ras <- rast(list.files(
    path = here::here("data",
                      "processed",
                      "circuitscape_2080"),
    pattern = paste0(x, "_cum_curmap.asc$"),
    full.names = TRUE,
    recursive = TRUE
  ))
  ras_m <- mask(ras, nodes_all, inverse = TRUE)
  ras_m_1000 <- (ras_m/max(values(ras_m), na.rm = T)*1000) |> mask(ras_mask)
  
  ggplot() + 
  stars::geom_stars(data = stars::st_as_stars(ras_m_1000)) + 
  scale_fill_gradientn(
     colours = viridis::viridis(10),
     values = scales::rescale(quantile(values(ras_m_1000),
                              probs = seq(0, 1, 0.1),
                                       na.rm = T)),
    na.value = "transparent", 
    name = "") + 
      ggplot2::coord_sf(expand = FALSE) +
    ggnewscale::new_scale_fill() +
  geom_sf(data = nodes_all, fill = "grey70", color = NA) +  
   ggtitle("Circuitscape Maps 2080") + 
  theme_void()

ggsave(here("plots", "circuitscape_plots_2080", paste0("circuitscape_2080_sp", x,".png")), dpi = 300)
})


```


</details>


***

<details><summary>Session Info</summary>

```{r sessionInfo}
## DO NOT REMOVE!
Sys.time()
#git2r::repository() ## uncomment if you are using GitHub
sessionInfo()
```

</details>
