---
title: "least cost path results with statistics" 

author:
    - name: "Moritz Wenzler-Meya"
      url: 
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 
    - name: "Stephanie Kramer-Schadt"
      url: 
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id:
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate
        code_folding: false  
        toc: true            
        toc_depth: 2         
        
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
                      dev = "ragg_png", fig.width = 9, fig.height = 6, dpi = 600, retina = 1)
Sys.setlocale("LC_TIME", "C")
```

# Setup


```{r}
sapply(list("sf", "ggplot2", "ggeffects", "stringr", "dplyr", "foreign", "ggpubr", "here", "tmap", "raster", "d6", "viridis", "viridisLite", "pander"), 
       library, character.only = TRUE, logical.return = TRUE)
```

# NOT RUN 
# Summary

The following summary is based on the 75% cut off file done by Matt Struebig outside this repository in GIS. 

```{r}
lcp_join_2020 <- st_read(here("data", "processed", "lcp_join", "lcp_join_2020.gpkg"))
lcp_join_2050 <- st_read(here("data", "processed", "lcp_join", "lcp_join_2050.gpkg"))
lcp_join_2080 <- st_read(here("data", "processed", "lcp_join", "lcp_join_2080.gpkg"))
```

# create all_data

```{r}
lcp_join_2020_sub <- lcp_join_2020  %>%
  group_by(spec_id, spec_tax, year) %>%
  summarize(n_cor = n(),
            len_sum = round(sum(len, na.rm = T)/1000, digits = 2), # convert to km
            len_mean = round(mean(len, na.rm = T)/1000, digits = 2), # convert to km
            hsi_mean =round(mean(hsi_mean_cur, na.rm = T)/1000, digits = 2),
            hsi_sum =round(sum(hsi_sum_cur, na.rm = T)/1000, digits = 2),
            cs_mean = round(mean(circ_mean_cur, na.rm = T), digits = 2),
            forest_prop = round(mean(num_forest_cur/(len/1000), na.rm = T), digits = 2),  # convert to km
            forest_prop_cur = round(mean(num_forest_cur/(len/1000), na.rm = T), digits = 2), # convert to km
            forest_prop_lc_2050 = round(mean(num_forest_2050/(len/1000), na.rm = T), digits = 2), # convert to km
            forest_prop_lc_2080 = round(mean(num_forest_2080/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_opp_mean_km = round(mean(cost_oppcost_sum_cur, na.rm = T), digits = 2),
            cost_resto_mean_km = round(mean(cost_resto_sum_cur, na.rm = T), digits = 2),
            cost_resto_mean_km_cur = round(mean(cost_resto_sum_cur, na.rm = T), digits = 2),
            cost_resto_mean_km_lc_2050 = round(mean(cost_resto_sum_lc_2050, na.rm = T), digits = 2),
            cost_resto_mean_km_lc_2080 = round(mean(cost_resto_sum_lc_2080, na.rm = T), digits = 2),
            cost_resto_sum_km = round(sum(cost_resto_sum_cur, na.rm = T), digits = 2),
            cost_resto_sum_km_cur = round(sum(cost_resto_sum_cur, na.rm = T), digits = 2),
            cost_resto_sum_km_lc_2050 = round(sum(cost_resto_sum_lc_2050, na.rm = T), digits = 2),
            cost_resto_sum_km_lc_2080 = round(sum(cost_resto_sum_lc_2080, na.rm = T), digits = 2),
            cost_div_len_opp_km = round(mean(cost_oppcost_sum_cur/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km = round(sum(cost_resto_sum_cur/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km_cur = round(sum(cost_resto_sum_cur/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km_lc_2050 = round(sum(cost_resto_sum_lc_2050/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km_lc_2080 = round(sum(cost_resto_sum_lc_2080/(len/1000), na.rm = T), digits = 2), # convert to km
            t10_mean = round(mean(t_10_mean_cur , na.rm = T), digits = 2),
            t10_mean_cur = round(mean(t_10_mean_cur , na.rm = T), digits = 2),
            t10_mean_lc_2050 = round(mean(t_10_mean_2050 , na.rm = T), digits = 2),
            t10_mean_lc_2080 = round(mean(t_10_mean_2080 , na.rm = T), digits = 2),
            t25_mean = round(mean(t_25_mean_cur, na.rm = T), digits = 2),
            t25_mean_cur = round(mean(t_25_mean_cur, na.rm = T), digits = 2),
            t25_mean_lc_2050 = round(mean(t_25_mean_2050, na.rm = T), digits = 2),
            t25_mean_lc_2080 = round(mean(t_25_mean_2080, na.rm = T), digits = 2),
            cost_div_num = round(mean(cost_resto_sum_cur/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_div_num_cur = round(mean(cost_resto_sum_cur/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_div_num_lc_2050 = round(mean(cost_resto_sum_lc_2050/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_div_num_lc_2080 = round(mean(cost_resto_sum_lc_2080/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_opp_div_num = round(mean(cost_oppcost_sum_cur/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_all_div = round((mean(cost_oppcost_sum_cur, na.rm = T))+(mean(cost_resto_sum_cur, na.rm = T)), digits = 2),
            cost_all_div_num = round((mean(cost_oppcost_sum_cur/n_cor, na.rm = T))+(mean(cost_resto_sum_cur/n_cor, na.rm = T)),  digits = 2) # divided by number of corridors
  ) %>% data.frame()

lcp_join_2050_sub <- lcp_join_2050  %>%
  group_by(spec_id, spec_tax, year) %>%
  summarize(n_cor = n(),
            len_sum = round(sum(len, na.rm = T)/1000, digits = 2), # convert to km
            len_mean = round(mean(len, na.rm = T)/1000, digits = 2), # convert to km
            hsi_mean =round(mean(hsi_mean_lc_2050, na.rm = T)/1000, digits = 2),
            hsi_sum =round(sum(hsi_sum_lc_2050, na.rm = T)/1000, digits = 2),
            cs_mean = round(mean(circ_mean_lc_2050, na.rm = T), digits = 2),
            forest_prop_cur = round(mean(num_forest_cur/(len/1000), na.rm = T), digits = 2), # convert to km
            forest_prop = round(mean(num_forest_2050/(len/1000), na.rm = T), digits = 2), # convert to km
            forest_prop_lc_2050 = round(mean(num_forest_2050/(len/1000), na.rm = T), digits = 2), # convert to km
            forest_prop_lc_2080 = round(mean(num_forest_2080/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_opp_mean_km = round(mean(cost_oppcost_sum_lc_2050, na.rm = T), digits = 2),
            cost_resto_mean_km_cur = round(mean(cost_resto_sum_cur, na.rm = T), digits = 2),
            cost_resto_mean_km = round(mean(cost_resto_sum_lc_2050, na.rm = T), digits = 2),
            cost_resto_mean_km_lc_2050 = round(mean(cost_resto_sum_lc_2050, na.rm = T), digits = 2),
            cost_resto_mean_km_lc_2080 = round(mean(cost_resto_sum_lc_2080, na.rm = T), digits = 2),
            cost_resto_sum_km_cur = round(sum(cost_resto_sum_cur, na.rm = T), digits = 2),
            cost_resto_sum_km = round(sum(cost_resto_sum_lc_2050, na.rm = T), digits = 2),
            cost_resto_sum_km_lc_2050 = round(sum(cost_resto_sum_lc_2050, na.rm = T), digits = 2),
            cost_resto_sum_km_lc_2080 = round(sum(cost_resto_sum_lc_2080, na.rm = T), digits = 2),
            cost_div_len_opp_km = round(mean(cost_oppcost_sum_lc_2050/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km_cur = round(sum(cost_resto_sum_cur/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km = round(sum(cost_resto_sum_lc_2050/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km_lc_2050 = round(sum(cost_resto_sum_lc_2050/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km_lc_2080 = round(sum(cost_resto_sum_lc_2080/(len/1000), na.rm = T), digits = 2), # convert to km
            t10_mean_cur = round(mean(t_10_mean_cur , na.rm = T), digits = 2),
            t10_mean = round(mean(t_10_mean_2050 , na.rm = T), digits = 2),
            t10_mean_lc_2050 = round(mean(t_10_mean_2050 , na.rm = T), digits = 2),
            t10_mean_lc_2080 = round(mean(t_10_mean_2080 , na.rm = T), digits = 2),
            t25_mean_cur = round(mean(t_25_mean_cur, na.rm = T), digits = 2),
            t25_mean = round(mean(t_25_mean_2050, na.rm = T), digits = 2),
            t25_mean_lc_2050 = round(mean(t_25_mean_2050, na.rm = T), digits = 2),
            t25_mean_lc_2080 = round(mean(t_25_mean_2080, na.rm = T), digits = 2),
            cost_div_num_cur = round(mean(cost_resto_sum_cur/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_div_num = round(mean(cost_resto_sum_lc_2050/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_div_num_lc_2050 = round(mean(cost_resto_sum_lc_2050/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_div_num_lc_2080 = round(mean(cost_resto_sum_lc_2080/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_opp_div_num = round(mean(cost_oppcost_sum_lc_2050/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_all_div = round((mean(cost_oppcost_sum_lc_2050, na.rm = T))+(mean(cost_oppcost_sum_lc_2050, na.rm = T)), digits = 2),
            cost_all_div_num = round((mean(cost_oppcost_sum_lc_2050/n_cor, na.rm = T))+(mean(cost_resto_sum_lc_2050/n_cor, na.rm = T)), digits = 2) # divided by number of corridors
  ) %>% data.frame()

lcp_join_2080_sub <- lcp_join_2080  %>%
  group_by(spec_id, spec_tax, year) %>%
  summarize(n_cor = n(),
            len_sum = round(sum(len, na.rm = T)/1000, digits = 2), # convert to km
            len_mean = round(mean(len, na.rm = T)/1000, digits = 2), # convert to km
            hsi_mean =round(mean(hsi_mean_lc_2080, na.rm = T)/1000, digits = 2),
            hsi_sum =round(sum(hsi_sum_lc_2080, na.rm = T)/1000, digits = 2),
            cs_mean = round(mean(circ_mean_lc_2080, na.rm = T), digits = 2),
            forest_prop_cur = round(mean(num_forest_cur/(len/1000), na.rm = T), digits = 2), # convert to km
            forest_prop_lc_2050 = round(mean(num_forest_2050/(len/1000), na.rm = T), digits = 2), # convert to km
            forest_prop = round(mean(num_forest_2080/(len/1000), na.rm = T), digits = 2), # convert to km
            forest_prop_lc_2080 = round(mean(num_forest_2080/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_opp_mean_km = round(mean(cost_oppcost_sum_lc_2080, na.rm = T), digits = 2),
            cost_resto_mean_km_cur = round(mean(cost_resto_sum_cur, na.rm = T), digits = 2),
            cost_resto_mean_km_lc_2050 = round(mean(cost_resto_sum_lc_2050, na.rm = T), digits = 2),
            cost_resto_mean_km = round(mean(cost_resto_sum_lc_2080, na.rm = T), digits = 2),
            cost_resto_mean_km_lc_2080 = round(mean(cost_resto_sum_lc_2080, na.rm = T), digits = 2),
            cost_resto_sum_km_cur = round(sum(cost_resto_sum_cur, na.rm = T), digits = 2),
            cost_resto_sum_km_lc_2050 = round(sum(cost_resto_sum_lc_2050, na.rm = T), digits = 2),
            cost_resto_sum_km = round(sum(cost_resto_sum_lc_2080, na.rm = T), digits = 2),
            cost_resto_sum_km_lc_2080 = round(sum(cost_resto_sum_lc_2080, na.rm = T), digits = 2),
            cost_div_len_opp_km = round(mean(cost_oppcost_sum_lc_2080/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km_cur = round(sum(cost_resto_sum_cur/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km_lc_2050 = round(sum(cost_resto_sum_lc_2050/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km = round(sum(cost_resto_sum_lc_2080/(len/1000), na.rm = T), digits = 2), # convert to km
            cost_div_len_resto_km_lc_2080 = round(sum(cost_resto_sum_lc_2080/(len/1000), na.rm = T), digits = 2), # convert to km
            t10_mean_cur = round(mean(t_10_mean_cur , na.rm = T), digits = 2),
            t10_mean_lc_2050 = round(mean(t_10_mean_2050 , na.rm = T), digits = 2),
            t10_mean = round(mean(t_10_mean_2080 , na.rm = T), digits = 2),
            t10_mean_lc_2080 = round(mean(t_10_mean_2080 , na.rm = T), digits = 2),
            t25_mean_cur = round(mean(t_25_mean_cur, na.rm = T), digits = 2),
            t25_mean_lc_2050 = round(mean(t_25_mean_2050, na.rm = T), digits = 2),
            t25_mean = round(mean(t_25_mean_2080, na.rm = T), digits = 2),
            t25_mean_lc_2080 = round(mean(t_25_mean_2080, na.rm = T), digits = 2),
            cost_div_num_cur = round(mean(cost_resto_sum_cur/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_div_num_lc_2050 = round(mean(cost_resto_sum_lc_2050/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_div_num = round(mean(cost_resto_sum_lc_2080/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_div_num_lc_2080 = round(mean(cost_resto_sum_lc_2080/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_opp_div_num = round(mean(cost_oppcost_sum_lc_2080/n_cor, na.rm = T), digits = 2), # divided by number of corridors
            cost_all_div = round((mean(cost_oppcost_sum_lc_2080, na.rm = T))+(mean(cost_oppcost_sum_lc_2080, na.rm = T)), digits = 2),
            cost_all_div_num = round((mean(cost_oppcost_sum_lc_2080/n_cor, na.rm = T))+(mean(cost_resto_sum_lc_2080/n_cor, na.rm = T)), digits = 2) # divided by number of corridors
  ) %>% data.frame()


all_data <- rbind(lcp_join_2020_sub, lcp_join_2050_sub, lcp_join_2080_sub)
```

## load nodes

```{r}
all_data_list <- split(all_data, seq(nrow(all_data)))

fun_num_node <- function(x){
  year <- x$year
  id <- x$spec_id
  node <- st_read(here("data", "processed", "node_layers", paste0("nodes_", year),
                           paste0("nodes_", year,"_species_", id, ".gpkg")))
  x$n_node <- nrow(node)
  return(x)
}

all_data_2 <- do.call(rbind, lapply(all_data_list, fun_num_node))

saveRDS(all_data_2, here("output", "lcp_trends_20240722.RDS"))
```

# END NOT RUN 

## Rename all_data to lcp_trends and save without geometry as csv

# load data for statistics

```{r}
#lcptrends <- readRDS(here("output", "lcp_trends_all.RDS"))
lcptrends <- readRDS(here("data", "processed", "lcp_trends_all.RDS")) |> dplyr::select(!geom)

```


# Statistics 

## number of nodes

```{r}
lcptrends$response <- lcptrends$n_node #change here!

lcptrends %>%
    group_by(year,spec_tax) %>% 
    summarise(median = median(response)) 


my_model <- glm(response ~ year*spec_tax, family = 'poisson', data = lcptrends) ## change depending on response
pander(summary(my_model))
(summary(my_model))

a <- ggpredict(my_model, terms = c("year", "spec_tax")) |> plot()
a +labs(y= "number of nodes", x = "time slice", title = '') + ## change 
   theme_d6(bg = "white") + 
   theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))
ggsave(path = here("plots", "lcp_statistics"), filename = "glm_num_nodes.png", device = "png",
       width = 6, height = 8)
```

## number of corridors

```{r}
lcptrends$response <- lcptrends$n_cor #change response here!

lcptrends %>%
    group_by(year,spec_tax) %>% 
    summarise(median = median(response)) 


my_model <- glm(response ~ year*spec_tax, family = 'poisson', data = lcptrends) ## change family depending on response
pander(summary(my_model))
(summary(my_model))

a <- ggpredict(my_model, terms = c("year", "spec_tax")) |> plot()
a +labs(color= 'Taxon',y= "number of corridors", x = "time slice", title = '') + ## change 
   theme_d6(bg = "white") + 
   theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))
ggsave(path = here("plots", "lcp_statistics"), filename = "glm_num_cors.png", device = "png", ##change
       dpi=300)
```

## total length

```{r}
lcptrends$response <- lcptrends$len_sum #change response here!

lcptrends %>%
    group_by(year,spec_tax) %>% 
    summarise(median = median(response)) 


my_model <- glm(response ~ year*spec_tax, family = Gamma(link="log"), data = lcptrends) ## change family depending on response
#pander(summary(my_model))
(summary(my_model))

a <- ggpredict(my_model, terms = c("year", "spec_tax")) |> plot()
a +labs(color= 'Taxon',y= "total length", x = "time slice", title = '') + ## change 
   theme_d6(bg = "white") + 
   theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))
ggsave(path = here("plots", "lcp_statistics"), filename = "glm_tot_length.png", device = "png", ##change
       width = 6, height = 8)
```


## HSI mean

```{r}
lcptrends$response <- lcptrends$hsi_mean #change response here!

lcptrends %>%
    group_by(year,spec_tax) %>% 
    summarise(median = median(response)) 


my_model <- glm(response ~ year*spec_tax, family = 'binomial', data = lcptrends) ## change family depending on response
#pander(summary(my_model))
(summary(my_model))

a <- ggpredict(my_model, terms = c("year", "spec_tax")) |> plot()
a +labs(color= 'Taxon',y= "mean HSI", x = "time slice", title = '') + ## change 
   theme_d6(bg = "white") + 
   theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))
ggsave(path = here("plots", "lcp_statistics"), filename = "glm_mean_hsi.png", device = "png", ##change
       width = 6, height = 8)
```


## Proportion of corridor forested

Approximating a proportion, because we calculated the number of forested cells underlying a corridor line. If diagonal, this could be two forest cells that are cut by the corridor line. In that case, we reset the proportion to 1.
```{r}
lcptrends$response <- lcptrends$forest_prop #change response here!
range(lcptrends$forest_prop) ## 6 corridors have prob > 1....
dummy <- which(lcptrends$forest_prop > 1) ; lcptrends[dummy,]
lcptrends$forest_prop[dummy] <- 1
lcptrends$response <- lcptrends$forest_prop #set again


lcptrends %>%
    group_by(year,spec_tax) %>% 
    summarise(median = median(response)) 


my_model <- glm(response ~ year*spec_tax, family = 'binomial', data = lcptrends) ## change family depending on response
#pander(summary(my_model))
(summary(my_model))

a <- ggpredict(my_model, terms = c("year", "spec_tax")) |> plot()
a +labs(color= 'Taxon',y= "prop. corridors forested", x = "time slice", title = '') + ## change 
   theme_d6(bg = "white") + 
   theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))
ggsave(path = here("plots", "lcp_statistics"), filename = "glm_prop_for.png", device = "png", ##change
       width = 6, height = 8)
```



## Restoration costs mean

```{r}
lcptrends$response <- lcptrends$cost_div_num/10 #cost_resto_mean_km #change response here!

lcptrends %>%
    group_by(year,spec_tax) %>% 
    summarise(median = median(response)) 


my_model <- glm(response ~ year*spec_tax, family = Gamma('log'),  data = lcptrends) ## change family depending on response
#pander(summary(my_model))
(summary(my_model))

a <- ggpredict(my_model, terms = c("year", "spec_tax")) |> plot()
a +labs(color= 'Taxon',y= "restoration costs", x = "time slice", title = '') + ## change 
   theme_d6(bg = "white") + 
   theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))
ggsave(path = here("plots", "lcp_statistics"), filename = "glm_resto_costs.png", device = "png", ##change
       width = 6, height = 8)
```


## Opportunity costs mean

```{r}
lcptrends$response <- lcptrends$cost_opp_div_num/1000 #change response here!

lcptrends %>%
    group_by(year,spec_tax) %>% 
    summarise(median = median(response)) 


my_model <- glm(response ~ year*spec_tax, family = Gamma('log'), data = lcptrends) ## change family depending on response
#pander(summary(my_model))
(summary(my_model))

a <- ggpredict(my_model, terms = c("year", "spec_tax")) |> plot()
a +labs(color= 'Taxon',y= "opportunity costs / 1000", x = "time slice", title = '') + ## change 
   theme_d6(bg = "white") + 
   theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))
ggsave(path = here("plots", "lcp_statistics"), filename = "glm_opp_costs.png", device = "png", ##change
       width = 6, height = 8)
```


# Boxplots in d6 theme

Figure 2

```{r}
library(d6)

d6::theme_d6()
```

## number of nodes

```{r}
bp_node <- 
  ggplot(lcptrends, aes(x=as.factor(year), y=n_node)) +
  geom_boxplot(outlier.size = -1, position=position_dodge(0.9), fill = "grey90") +
  coord_cartesian(ylim = c(0,380)) +
  labs(x = "Timeslice", y = "") + # add y axis name if you want
  geom_jitter(aes(color=as.factor(spec_tax)), shape=16, position=position_jitter(0.2), alpha =0.9, size = 3.3) +
  scale_color_viridis_d(option = "viridis") + # other colorpalettes didn't fit that good. Some colors were too bright. Turbo is an option
  labs(color='Taxon', title = "a) Number of nodes") +
  theme_d6(bg = "white") + # the background can be transparent if needed
  theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))

ggsave(bp_node, path = here("plots"), filename = "Fig2a_boxplot_num_nodes_viridis.png", device = "png",
       width = 6,
       height = 8)
```

## number of corridors

```{r}
bp_cor <- 
  ggplot(lcptrends, aes(x=as.factor(year), y=n_cor)) +
  geom_boxplot(outlier.size = -1, position=position_dodge(0.9), fill = "grey90") +
  labs(x = "Timeslice", y = "") +
  geom_jitter(aes(color=as.factor(spec_tax)), shape=16, position=position_jitter(0.2), alpha =0.9, size = 3.3) +
  scale_color_viridis_d(option = "viridis") + 
  labs(color='Taxon', title = "b) Number of corridors") +
  theme_d6(bg = "white") +
  theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))

ggsave(bp_cor, path = here("plots"), filename = "Fig2b_boxplot_num_corridors_viridis.png", device = "png",
       width = 6,
       height = 8)

```

## sum of length

```{r}
bp_sum_len <- 
  ggplot(lcptrends, aes(x=as.factor(year), y=len_sum)) +
  geom_boxplot(outlier.size = -1, position=position_dodge(0.9), fill = "grey90") +
  labs(x = "Timeslice", y = "") +
  geom_jitter(aes(color=as.factor(spec_tax)), shape=16, position=position_jitter(0.2), alpha =0.9, size = 3.3) +
  scale_color_viridis_d(option = "viridis") + 
  labs(color='Taxon', title = "c) Sum of length") +
  theme_d6(bg = "white") +
  theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))

ggsave(bp_sum_len, path = here("plots"), 
       filename = "Fig2c_boxplot_sum_of_length_viridis.png", 
       device = "png",
       width = 6,
       height = 8)

```


## mean hsi

```{r}
bp_mean_hsi <- 
  ggplot(lcptrends, aes(x=as.factor(year), y=hsi_mean)) +
  geom_boxplot(outlier.size = -1, position=position_dodge(0.9), fill = "grey90") +
  coord_cartesian(ylim = c(0.3,0.8)) +
  labs(x = "Timeslice", y = "") +
  geom_jitter(aes(color=as.factor(spec_tax)), shape=16, position=position_jitter(0.2), alpha =0.9, size = 3.3) +
  scale_color_viridis_d(option = "viridis") + 
  labs(color='Taxon', title = "d) Mean HSI") +
  theme_d6(bg = "white") +
  theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))

ggsave(bp_mean_hsi, path = here("plots"), 
       filename = "Fig2d_boxplot_mean_hsi_viridis.png", 
       device = "png",
       width = 6,
       height = 8)

```

## proportion of forest

```{r}
bp_prop_for <- 
  ggplot(lcptrends, aes(x=as.factor(year), y=forest_prop)) +
  geom_boxplot(outlier.size = -1, position=position_dodge(0.9), fill = "grey90") +
  coord_cartesian(ylim = c(0,1)) +
  labs(x = "Timeslice", y = "") +
  geom_jitter(aes(color=as.factor(spec_tax)), shape=16, position=position_jitter(0.2), alpha =0.9, size = 3.3) +
  scale_color_viridis_d(option = "viridis") + 
  labs(color='Taxon', title = "e) Proportion of forest") +
  theme_d6(bg = "white") +
  theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))

ggsave(bp_prop_for, path = here("plots"), 
       filename = "Fig2e_boxplot_prop_forest_viridis.png", 
       device = "png",
       width = 6,
       height = 8)

```

## mean restoration cost divided by the number of corridors

```{r}
bp_mean_resto_cost <- 
  ggplot(lcptrends, aes(x=as.factor(year), y=cost_div_num/10)) +
  geom_boxplot(outlier.size = -1, position=position_dodge(0.9), fill = "grey90") +
  coord_cartesian(ylim = c(0, 250)) +
  labs(x = "Timeslice", y = "") +
  geom_jitter(aes(color=as.factor(spec_tax)), shape=16, position=position_jitter(0.2), alpha =0.9, size = 3.3) +
  scale_color_viridis_d(option = "viridis") + 
  labs(color='Taxon', title = "f) Mean restoration costs divided by the\nnumber of corridors (1000s US$/km² and corridor)") +
  theme_d6(bg = "white")  +
  theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))

ggsave(bp_mean_resto_cost, path = here("plots"), 
       filename = "Fig2f_boxplot_mean_resto_cost_divided_by_n_corridor_viridis.png", 
       device = "png",
       width = 6,
       height = 8)
```

## mean opportunity cost divided by the number of corridors

```{r}
bp_mean_opp_cost <- 
  ggplot(lcptrends, aes(x=as.factor(year), y=cost_opp_div_num/1000)) +
  geom_boxplot(outlier.size = -1, position=position_dodge(0.9), fill = "grey90") +
  coord_cartesian(ylim = c(0, 3000)) +
  labs(x = "Timeslice", y = "") +
  geom_jitter(aes(color=as.factor(spec_tax)), shape=16, position=position_jitter(0.2), alpha =0.9, size = 3.3) +
  scale_color_viridis_d(option = "viridis") + 
  labs(color='Taxon', title = "g) Mean opportunity costs divided by the\nnumber of corridors (1000s US$/km² and corridor)") +
  theme_d6(bg = "white")  +
  theme(legend.position = c(1.5, 0.8), 
        axis.text.y = element_text(angle = 90, hjust = 0.5),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 14),
        plot.title = element_text(size=14))

ggsave(bp_mean_opp_cost, path = here("plots"), 
       filename = "Fig2g_boxplot_mean_opp_cost_divided_by_n_corridor_viridis.png", 
       device = "png",
       width = 6,
       height = 8)
```

#END#
